### 2019-10-08 defesa/tex/chapter/e3p.tex
wip

Using the identity $x = \tan{\frac{\theta}{2}}$ it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$. The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots. A possible approach, as described by \citeonline[p.~191]{horn}, is to find all the eigenvalues of a matrix related to the polynomial called the companion matrix. There are methods that do that fairly efficiently with the observation that roots which are not close to the origin are susceptible to large errors and some times can not be found, this indeed happened in practice, as for some instances the method did not find roots which were priorly known. Another possibility would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method cannot converge. Nevertheless, a result published by \citeonline{mc1} says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.

@@

One of the greatest qualities of Chebyshev polynomials is its numerical stability. \citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{$p_n$ is in the power form or the monomial form if it can be written as $p_n=\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$. On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.

@@

Then, the Chebyshev interpolation of a function $f: [a, b] \mapsto \R$ can be determined using Lagrange's formula and the points $\hat{x}_1, \dots, \hat{x}_n$. 
As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called companion matrix. For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.

An alternative method can be found in \citeonline{boyd:2013}. It turns out that the Chebyshev interpolation can be calculated directly as a truncated Chebyshev series in $\bigO(n^2)$. Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial. Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials which have great numerical stability.

>>>>

Using the identity $x = \tan{\frac{\theta}{2}}$, it is possible to convert $\xi(\theta)$ on \autoref{eq:circumscribed_circle_b} into a univariate polynomial of degree $12$. The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula to determine their roots. A possible approach, as described by \citeonline[p.~191]{horn}, is to find all the eigenvalues of a matrix related to the polynomial called the companion matrix. 
In general, finding all the eigenvalues of a matrix is not easy, however, companion matrices have a special form which allows their eigenvalues to be found through a QR decomposition, a $\bigO(n^2)$ algorithm can be found in \citeonline{bini:2007}.
 The only problem is that for degree $12$ polynomials, roots which are not close to the origin are susceptible to large errors and some times can not be found. This indeed happened in practice, as for some instances the method did not find roots which were priorly known. Another possibility would be to use root-finding iterative methods, such as Newton's method, to approximate a root $\hat{x}$, divide the polynomial by $(x-\hat{x})$, and apply the method again until the method cannot converge. A result published by \citeonline{mc1}, however, says that iterative methods generally are not convergent for polynomials of degree $4$ or more, and also, the process of dividing the polynomial by $(x-\hat{x})$ carries along a lot of error, which could make the method, even if convergent, find spurious roots.

@@

One of the greatest qualities of Chebyshev polynomials is its numerical stability. \citeonline{gautschi:1979} showed that the matrix that maps polynomials onto its coefficients written in the power form\footnote{A polynomial is in the power form or the monomial form if it can be written as $\sum_{j=0}^{n}a_jx^j$} has a condition number that grows exponentially with $n$. On the other hand, the matrix that converts polynomials to the Chebyshev basis as \autoref{eq:chebseries}, has a linear condition number bounded by $\sqrt{2}n$.

@@

Then, the Chebyshev interpolation of a function $f: [a, b] \mapsto \R$ can be determined using Lagrange's formula and the points $\hat{x}_1, \dots, \hat{x}_n$. 
As it was mentioned, finding the roots of a polynomial written in the monomial form can be done by determining the eigenvalues of a so-called Frobenius companion matrix. For small $n$ this works fine, however, converting the polynomial obtained by \autoref{eq:lagrange} to the power form, as $n$ grows, becomes a very ill-conditioned problem.

An alternative method can be found in \citeonline{boyd:2013}. It turns out that the Chebyshev interpolation can be calculated directly as a truncated Chebyshev series in $\bigO(n^2)$. Also, given a polynomial written in the Chebyshev basis, a $n\times n$ matrix can be constructed, such that its eigenvalues are the roots of that polynomial, the author refers to this matrix as the Chebyshev-Frobenius companion matrix. Therefore, the whole process of interpolating and finding the roots can be done using only Chebyshev polynomials which have great numerical stability. Also, Chebyshev-Frobenius matrices have the same property as companion matrices which allows their eigenvalues to be found by a QR decomposition. Summing the two steps, a $\bigO(n^2)$ algorithm can be achieved.
